Model LF

### 2023-03-13 paper version Hamid test.Rmd
Commit

COMMENT> 
IDENTITY> xk_ds
EQ> xk_ds= xk_ds_used
if> disc <= 0
IDENTITY> xk_ds
EQ> xk_ds= xk_ds_disc
if> disc > 0

@@

COMMENT> 
IDENTITY> i_bd_nfc_k_ds
EQ> i_bd_nfc_k_ds= i_bd_nfc_k_ds_used
if> disc <= 0
IDENTITY> i_bd_nfc_k_ds
EQ> i_bd_nfc_k_ds= i_bd_nfc_k_ds_disc
if> disc > 0

@@

@@

>>>>

COMMENT> 
IDENTITY> xk_ds
EQ> xk_ds= xk_ds_used

@@

COMMENT> 
IDENTITY> i_bd_nfc_k_ds
EQ> i_bd_nfc_k_ds= i_bd_nfc_k_ds_used

@@

# Discussion

## Baseline

```{r}
shock_disc_model_shock=disc %>% window(start= c(2006,3))
```

```{r}
# Define add-factor list (defining shock)
constantAdjList_disc <- list(

 disc = TIMESERIES(shock_disc_model_shock+1 ,START=c(2006,3),  FREQ='Q'), 
shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Disc1 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                  ,ConstantAdjustment = constantAdjList_disc
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_Disc1 = Disc1$simulation$max_dp
wage_Disc1 = Disc1$simulation$wage
komp_r_Disc1 = Disc1$simulation$komp_r
part_Disc1 = Disc1$simulation$part
yk_ds_Disc1 = Disc1$simulation$yk_ds
pc_ds_Disc1 = Disc1$simulation$pc_ds
unemp_Disc1 = Disc1$simulation$unemp
dp_person_Disc1 = Disc1$simulation$dp_person
nl_g_Disc1 = Disc1$simulation$nl_g
ur_ds_Disc1 = Disc1$simulation$ur_ds

pconk_ds_Disc1 = Disc1$simulation$pconk_ds
ik_Disc1 = Disc1$simulation$ik
gk_Disc1 = Disc1$simulation$gk
xk_ds_Disc1 = Disc1$simulation$xk_ds
mk_ds_Disc1 = Disc1$simulation$mk_ds

AD_Disc1= pconk_ds_Disc1 + ik_Disc1 + gk_Disc1
TB_Disc1= xk_ds_Disc1 - mk_ds_Disc1
```

```{r}
# Define add-factor list (defining shock)
constantAdjList_disc1_shock <- list(
  disc = TIMESERIES(shock_disc_model_shock+1 ,START=c(2006,3),  FREQ='Q'), 
shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

```{r}
# Simulate the model (following shock)
Disc1_shock <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_disc1_shock
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_Disc1_s = Disc1_shock$simulation$max_dp
wage_Disc1_s = Disc1_shock$simulation$wage
komp_r_Disc1_s = Disc1_shock$simulation$komp_r
part_Disc1_s = Disc1_shock$simulation$part
yk_ds_Disc1_s = Disc1_shock$simulation$yk_ds
pc_ds_Disc1_s = Disc1_shock$simulation$pc_ds
unemp_Disc1_s = Disc1_shock$simulation$unemp
dp_person_Disc1_s = Disc1_shock$simulation$dp_person
nl_g_Disc1_s = Disc1_shock$simulation$nl_g
ur_ds_Disc1_s = Disc1_shock$simulation$ur_ds

pconk_ds_Disc1_s = Disc1_shock$simulation$pconk_ds
ik_Disc1_s = Disc1_shock$simulation$ik
gk_Disc1_s = Disc1_shock$simulation$gk
xk_ds_Disc1_s = Disc1_shock$simulation$xk_ds
mk_ds_Disc1_s = Disc1_shock$simulation$mk_ds

AD_Disc1_s= pconk_ds_Disc1_s + ik_Disc1_s + gk_Disc1_s
TB_Disc1_s= xk_ds_Disc1_s - mk_ds_Disc1_s

@@

## Disc

plot(window((ur_ds_Disc1_s - ur_ds_Disc1)*100, start= 2014), col= "blue", xlab= "Year", ylab= "percentage change from baseline", main= "Test", ylim= c(-0.02,0.015));
lines(window(((yk_ds_Disc1_s - yk_ds_Disc1) / yk_ds_Disc1)*100, start= 2014), col= "green");
legend("left", legend=c("Unemployment rate","GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

plot(window(AD_Disc1_s - AD_Disc1, start= 2014), col= "blue", xlab= "Year", ylab= "Level change from baseline", main= "Sensitivity 2", ylim= c(-100,100));
lines(window(TB_Disc1_s - TB_Disc1, start= 2014), col= "green");
legend("left", legend=c("Aggregate demand","Trade balance"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

```{r}
plot(window(nl_g_Disc1_s - nl_g_Disc1, start= 2014), col= "blue", xlab= "Year", ylab= "Level change", main= "Sensitivity 2");
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```
